\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[default]{raleway}
\usepackage[T1]{fontenc}
\usepackage[a4paper]{geometry}
\geometry{top=1.25cm, bottom=1.25cm, left=1.5cm, right=1.5cm}
\setlength{\parindent}{0mm}

\definecolor{sectcol}{RGB}{0,150,255}
\definecolor{softcol}{RGB}{225,225,225}

\titleformat{\section}{\normalfont\Large\bfseries\color{sectcol}}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries\color{sectcol}}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
    \Huge \textsc{Atiq Israk}\\[2pt]
    \normalsize Product Manager \\[5pt]
    \normalsize Gulshan-1, Dhaka, Bangladesh | +8801701893882 | \href{mailto:atiqisrak@gmail.com}{atiqisrak@gmail.com} \\[5pt]
    \normalsize \href{https://atiqisrak.vercel.app}{atiqisrak.vercel.app}
\end{center}

\section*{Objective}
Forward-thinking Product Manager with 6+ years of experience translating customer needs into profitable, user-centric solutions. Skilled in \textbf{product pricing}, \textbf{business strategy}, and \textbf{go-to-market planning}. Adept at defining user journeys, managing complex roadmaps, and balancing \textbf{revenue vs.\ cost} to align with business goals. Track record includes a 160\% boost in revenue through AI-driven customer engagement and \$60k in cost savings via process automation. Seeking to leverage strong leadership, data-driven decision-making, and Agile expertise to deliver high-impact digital products and mentor cross-functional teams.

\section*{Experience}

\subsection*{Ether Technologies | Product Manager}
\textit{June 2023 – Present}
\begin{itemize}[leftmargin=*]
    \item Develop the \textbf{product vision and strategy}, aligning user journey optimization, pricing, and feature sets with the company's broader objectives. 
    \item Oversee \textbf{go-to-market (GTM)} execution and marketing campaign planning, achieving a 20\% increase in new user acquisition within six months.
    \item Partner with leadership on \textbf{revenue vs.\ cost} analyses, ensuring product portfolios achieve profitability and sustainable growth metrics.
    \item Launch and manage \textbf{MAVE CMS} (SaaS, MACH architecture) and \textbf{AssetIQ}, reducing operational overhead by 20\% through strategic cost controls and efficient cloud resource usage.
    \item Drive cross-functional collaboration using \textbf{Lean Product Development} and Agile methods, elevating team productivity by 30\% while retaining high engineering quality.
\end{itemize}

\subsection*{Recent Projects:}
\begin{itemize}[leftmargin=*]
    \item \textbf{\href{https://mave.ethertech.ltd}{MAVE CMS (SaaS | API-First | MACH)}} \\
    Spearheaded the strategic and technical blueprint for an enterprise-grade headless CMS. Negotiated requirements with stakeholders to align product capabilities with market demand, and integrated microservices, GraphQL APIs, and CI/CD pipelines on AWS. Shortened deployment cycles by 30\%, enabling faster custom solutions and scalability.

\item \textbf{\href{https://assetiq.ethertech.ltd/}{Asset IQ (RFID-based Asset Management System)}} \\
Drove vision, strategy, and delivery of an enterprise RFID asset management platform for real-time tracking and lifecycle monitoring. Coordinated cross-functional teams to launch modules for asset onboarding, depreciation, maintenance, and compliance. Customized analytics dashboards for banks and NGOs, enabling audit-readiness, loss detection, and regulatory compliance across secure, scalable infrastructure.

    \item \textbf{\href{https://www.aranya.com.bd/}{Aranya (Fastest E-Commerce Platform)}} \\
    Led product discovery, user journey mapping, and release cycles for a NextJS-Redux platform. Collaborated with UI/UX designers to reduce friction points and improve site load times by 35\%. Introduced a phased rollout approach to manage risk and smooth stakeholder adoption, resulting in a 20\% increase in conversions.

    \item \textbf{\href{https://www.uhlbd.com/}{UHL (Dynamic Hospital Management System)}} \\
    Guided product requirements for digitizing patient pathways, from scheduling appointments to accessing reports. Streamlined real-time notifications and integrated secure record-keeping, boosting operational efficiency by 40\%. Conducted user acceptance testing with medical staff to refine workflows and enhance service delivery.

\end{itemize}

\subsection*{Navana Group | Technical Project Manager, Product \& Engineering}
\textit{August 2020 – March 2023}
\begin{itemize}[leftmargin=*]
    \item Oversaw a suite of AI-driven chatbot projects and digital transformation initiatives, unifying cross-departmental collaboration (Finance, Sales, IT) to launch products on time and within budget.
    \item Delivered \$20K+ in annual cost savings by optimizing containerized deployments (Docker) and implementing AWS best practices.
    \item Strengthened product vision by working with senior management to prioritize business strategies, leading to consecutive Best Employer awards for culture and collaboration.
\end{itemize}

\subsection*{Recent Projects:}
\begin{itemize}[leftmargin=*]
    \item \textbf{\href{https://gloriajeanscoffeesbd.com/menu}{Gloria Jean’s Coffees Bangladesh (E-Commerce)}} \\
    Drove the implementation of server load balancing, front-end enhancements, and process automation that collectively boosted sales by 27\%. Redesigned user flow to reduce checkout friction and accelerate client onboarding by 170\%.

    \item \textbf{\href{https://atiqisrak.vercel.app/}{NAVBOT (AI CRM Chatbot)}} \\
    Conceptualized and rolled out an AI-powered CRM chatbot targeting restaurants and vehicle servicing. Automated reservation and service request workflows, significantly cutting response times and improving the user satisfaction index.
\end{itemize}

\subsection*{TechCare Inc. | Frontend Web Developer}
\textit{February 2019 – July 2020}
\begin{itemize}[leftmargin=*]
    \item Developed and productized 120+ web templates using React/NextJS, amassing 863,000+ global downloads and over 430,000 purchases. 
    \item Leveraged Lottiefiles \& GSAP to create interactive experiences, increasing template conversion rates by 27\% and scaling the user base by 170\%.
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{University of Dhaka} – ACMP, Institute of Business Administration (2025)
    \item \textbf{Southeast University} – BSc in Computer Science and Engineering (2019)
    \item \textbf{Notre Dame College} – Science (2015)
\end{itemize}

\section*{Certifications}
\begin{itemize}[leftmargin=*]
    \item \textbf{\href{https://www.linkedin.com/learning/certificates/020adc39f55a9224f5c72e9ee45d56174b75337cb9834de2d45534c8ef2128e7}{Design Thinking}} – Microsoft \& PMI (2023)
    \item \textbf{\href{https://www.linkedin.com/learning/certificates/c94583d67c7b2c3bc4ac472c1c761f5f0dce6db0239049726cb0d69a3460eb0b}{Technical Project Management}} – PMI \& Microsoft (2023)
    \item \textbf{\href{https://www.linkedin.com/learning/certificates/f8a38ef54d303e8820573b3ec99589302564068a3af214ce0146c74161b64f6a}{Agile Software Development}} – LinkedIn (2023)
\end{itemize}

\section*{References}
\begin{minipage}[t]{0.45\textwidth}
    \textbf{Syed Yousuf Quadry} \\
    Product Manager \\
    Grameen Digital Healthcare Solutions
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
    \textbf{Abu Saem, FCA} \\
    Financial Controller \\
    Banglalink Digital
\end{minipage}

\end{document}
